Interactive plot for exploring results of Gaussian mean estimation experiments

### 2018-12-07 shiny/gauss_shiny.Rmd
A small revision to the Shiny plot accompanying text.

```{r create-shiny-plot, echo=FALSE, message=FALSE, warning=FALSE}
# Load the dplyr, ggplot and rmarkdown packages.
library(dplyr)
library(ggplot2)
library(cowplot)
library(rmarkdown)

@@

Spikes (sp)<br>
Bumps (bump)<br>
Blocks (blk)<br>
Angles (ang)<br>
Doppler (dop)<br>
Blip (blip)<br>
Corner (cor)

@@

Constant function (v1)<br>
Triple exponential (v2)<br>
Doppler (v3)<br>
Bumps (v4)<br>
Clipped Blocks (v5)

>>>>

```{r create-shiny-plot, echo=FALSE, message=FALSE, warning=FALSE}
# Load the packages.
library(dplyr)
library(ggplot2)
library(cowplot)
library(rmarkdown)
library(shiny)

@@

1. Spikes (sp)
2. Bumps (bump)
3. Blocks (blk)
4. Angles (ang)
5. Doppler (dop)
6. Blip (blip)
7. Corner (cor)

@@

1. Constant function (v1)
2. Triple exponential (v2)
3. Doppler (v3)
4. Bumps (v4)
5. Clipped Blocks (v5)
